An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-11 VLDB2026/main.tex
Add files via upload
Modify the reason why UNG multi-label construction single-label search performs poorly
 and try again.

\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG employs a distinct construction and search strategy, leading to a significant drop in query performance.

>>>>

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) The reason why UNG has poor performance is that each base vector has 8 attributes, but only one query attribute, which results in a large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
